Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-09-17 manu-draft.Rmd
adding co-authors

---
title: "Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Maya C. Burke (mburke@tbep.org), Emma E. Dontis (edontis@co.pinellas.fl.us), Jessica Lewis (jlewis@tbep.org), Miles Medina (miles.medina@ufl.edu), Elise Morrison (elise.morrison@essie.ufl.edu), Mark Rains (Mark.Rains@floridadep.gov), Gary E. Raulerson (graulerson@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org), David Tomasko (dave@sarasotabay.org), Joe Whalen (jwhalen@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---

>>>>

---
title: "Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
always_allow_html: true
bibliography: refs.bib
author: "Marcus W. Beck (mbeck@tbep.org), Andrew Altieri (andrew.altieri@essie.ufl.edu), Maya C. Burke (mburke@tbep.org), Diana W. Chin (diwchin@gmail.com), Emma E. Dontis (edontis@co.pinellas.fl.us), Jessica Lewis (jlewis@tbep.org), Miles Medina (miles.medina@ufl.edu), Elise Morrison (elise.morrison@essie.ufl.edu), Mark Rains (Mark.Rains@floridadep.gov), Gary E. Raulerson (graulerson@tbep.org), Sheila Scolaro (sscolar@tbep.org), Ed T. Sherwood (esherwood@tbep.org), David Tomasko (dave@sarasotabay.org), Nijole Wellendorf (nijole.wellendorf@floridadep.org), Joe Whalen (jwhalen@tbep.org)"
urlcolor: blue
csl: marine-pollution-bulletin.csl
link-citations: true
---
